%% thesis.tex 2014/04/11
%
% Based on sample files of unknown authorship.
%
% The Current Maintainer of this work is Paul Vojta.

\documentclass[masters]{ucbthesis}

\usepackage{biblatex}
\usepackage{rotating} % provides sidewaystable and sidewaysfigure

\usepackage[utf8]{inputenc}
\usepackage{amsmath,amsthm,amssymb}

\usepackage{mathtools}
\usepackage{bbm}
\usepackage{marvosym}
\usepackage[hidelinks]{hyperref}
\usepackage{framed}
\usepackage{enumitem}
\usepackage{float}
\usepackage{bm}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{url}


\newtheorem{theorem}{Theorem}[chapter]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{postulate}[theorem]{Postulate}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{observation}{Observation}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\vertiii}[1]{{\left\vert\kern-0.25ex\left\vert\kern-0.25ex\left\vert#1 
    \right\vert\kern-0.25ex\right\vert\kern-0.25ex\right\vert}}

\newcommand*\enlarg[2]{\bar{#1}_{#2}}
\newcommand*\cohnorm[1]{\vertiii{#1}^{\mathrm{coh}}_{K,\varphi,\alpha,\gamma}}

% To compile this file, run "latex thesis", then "biber thesis"
% (or "bibtex thesis", if the output from latex asks for that instead),
% and then "latex thesis" (without the quotes in each case).

% Double spacing, if you want it.  Do not use for the final copy.
% \def\dsp{\def\baselinestretch{2.0}\large\normalsize}
% \dsp

% If the Grad. Division insists that the first paragraph of a section
% be indented (like the others), then include this line:
% \usepackage{indentfirst}

\addtolength{\abovecaptionskip}{\baselineskip}

\bibliography{references}

\hyphenation{mar-gin-al-ia}
\hyphenation{bra-va-do}

\begin{document}

% Declarations for Front Matter

\title{On the Hairer-Caravenna-Zambotti Reconstruction}
\author{Viet-Duc Nguyen}
\degreesemester{Summer}
\degreeyear{2022}
\degree{Bachelor of Science}
\chair{Professor Peter K. Friz}
\othermembers{Professor Peter Bank}
% For a co-chair who is subordinate to the \chair listed above
% \cochair{Professor Benedict Francis Pope}
% For two co-chairs of equal standing (do not use \chair with this one)
% \cochairs{Professor Richard Francis Sony}{Professor Benedict Francis Pope}
\numberofmembers{3}
% Previous degrees are no longer to be listed on the title page.
% \prevdegrees{B.A. (University of Northern South Dakota at Hoople) 1978 \\
%   M.S. (Ed's School of Quantum Mechanics and Muffler Repair) 1989}
\field{Mathematics}
% Designated Emphasis -- this is optional, and rare
% \emphasis{Colloidal Telemetry}
% This is optional, and rare
% \jointinstitution{University of Western Maryland}
% This is optional (default is Berkeley)
% \campus{Berkeley}

% For a masters thesis, replace the above \documentclass line with
% \documentclass[masters]{ucbthesis}
% This affects the title and approval pages, which by default calls this
% document a "dissertation", not a "thesis".

\maketitle
% Delete (or comment out) the \approvalpage line for the final version.
% \approvalpage
\copyrightpage

\begin{alwayssingle}
\pagenumbering{gobble}
\section*{Zusammenfassung in deutscher Sprache}

Gegeben sei eine Familie von Distributionen \( (F_x)_{x \in \mathbb{R}^d} \). Gesucht ist eine Distribution, die für jeden Punkt \( x \in \mathbb{R}^d \) durch \( F_x \) lokal gut approximiert wird. Wir stellen das \emph{Reconstruction Theorem} vor, welches die Existenz sowie die Eindeutigkeit solch einer Distribution sichert. 

Das Problem ist von großer Bedeutung für die Behandlung stochastischer Differentialgleichungen; genauer ist es das zentrale Theorem der Theorie der \emph{Regularity Structures} von Martin Hairer, welche auch in diesem Zusammenhang zum ersten Mal bewiesen wurde. Wir geben einen alternativen Zugang zum Reconstruction Theorem, die ohne Regularity Structures auskommt. Stattdessen betten wir das Reconstruction Theorem in die Theorie der Distributionen ein.
Wir finden eine hinreichende und notwendige Bedingung für das Reconstruction Theorem, die wir \emph{coherence} nennen. Der Beweis des Reconstruction Theorems bildet das Kernstück dieser Arbeit. 

Als Anwendung des Reconstruction Theorems führen wir negative Hölderräume ein und beweisen das Sewing Lemma, ein wichtiges Hilfsmittel in der Theorie der rauen Pfade. Das Sewing Lemma wird oft als das eindimensionale Analogon des Reconstruction Theorems betrachtet. Wir überprüfen diese Aussage.

\end{alwayssingle}

\include{abstract}

\begin{frontmatter}

% You can delete the \clearpage lines if you don't want these to start on
% separate pages.

\tableofcontents
\clearpage
%\listoffigures
%\clearpage
%\listoftables


\end{frontmatter}

\pagestyle{headings}

% (Optional) \part{First Part}
\pagenumbering{arabic}

\include{chap1}
% \include{chap2}
\include{chap3}
\include{chap4}
\include{chap5}
\include{chap6}
\include{chap7}

\printbibliography

% \appendix
% \chapter{More Monticello Candidates}

\end{document}
